R Notebook for MSDepression Project

### 2022-09-03 lab_notebook/lab_notebook.Rmd
Add files via upload

#### 20220902
[] Cleaning script
  [] Sections
    [x] Initialize
    [x] read in data/subset
    [x] read in and handle promis scores, link to scan
    [x] Demographics
    [x] Define Depression Network
    [x] Network enrichment/disease within/outside depression network
    [x] Lesion Volume between diagnostic groups
    [x] Lesion burden between diagnostic groups
    [x] Interaction
    [x] Effect size x fascicle volume of overlap

#### 20220906
    [] Sensitivity Analyses

>>>>

#### 20220902
[] Cleaning script
  [] Sections
    [x] Initialize
    [x] read in data/subset
    [x] read in and handle promis scores, link to scan
    [x] Demographics
    [x] Define Depression Network
    [x] Network enrichment/disease within/outside depression network
    [x] Lesion Volume between diagnostic groups
    [x] Lesion burden between diagnostic groups
    [x] Interaction
    [x] Effect size x fascicle volume of overlap
    [x] Sensitivity Analyses

#### 20220906

    - add vol suffix
